Modelling spatial structure in small-area estimation

### 2022-08-03 src/docs_paper/paper.Rmd
Import CRPS results for simulation study straight into paper
Add metrics table for HIV survey results

@@

>>>>

## Results

```{r results="asis"}
#' Some of the lines should not be included
lines_remove <- c(1, 3, 4, 5)
cat(readLines("depends/crps-table-rho.txt")[-lines_remove], sep = "\n")
```

@@

## Results

```{r results="asis"}
#' Some of the lines should not be included
lines_remove <- c(1)
cat(readLines("depends/metric-table.txt")[-lines_remove], sep = "\n")
```
